Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
editing section 3
added delta to spin curves

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,L)$ be a tame log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;0)$. Then the
canonical ring

\begin{align*}
	R(\sx,L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

In this section, we will prove that if $(\sx , L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx',L'),(\sx,L)$ be tame, separably rooted log stacky spin
curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where

@@

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx',L')$ is a tame separably rooted log stacky spin
curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i'})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
			y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e_i >
		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
		generators for $I'$ together with any set of relations as in part (c)
		minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
Let $(\sx,L)$ and $(\sx',L')$ be the two log stacky spin curves in 
question, with coarse spaces $X = X'$. Define

>>>>

\subsection{Main Results}
These are our results.
\begin{thm}
\label{thm:g_0_generators_relations}
Let $(\sx,\Delta, L)$ be a tame log spin curve over a perfect field $k$, so
that $\sx$ has signature $\sigma = (0;e_1,\ldots, e_r;\delta)$. Then the
canonical ring

\begin{align*}
	R(\sx, \Delta, L) = \bigoplus_{d=0}^\infty H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

In this section, we will prove that if $(\sx , 0, L)$ is a spin curve,
so that $\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; 0)$, then
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1, \ldots,
e_r)$ with relations in degree at most $2e$, so long as $\sigma$ does
not lie in a finite list of exceptions. This is proven in
Subsection ~\ref{ssec:g_0_conclusion}. The proof is a rather
involved induction. In Subsections ~\ref{ssec:g_0_ram_pts},
~\ref{ssec:g_0_ram_orders} we prove inductive theorems, and in
Subsection ~\ref{ssec:g_0_base} we check the base cases of the
induction. Finally, in Subsection ~\ref{ssec:g_0_exceptional} we
list out the exceptional cases.

@@

\begin{defn}
\label{defn:admissible}
Let $(\sx', 0, L'),(\sx, 0, L)$ be tame, 
separably rooted log stacky spin
curves, both ramified over ramified at $Q_1,\ldots, Q_r$. Suppose
there is a birational map $\sx \rightarrow \sx'$, and let $J \subset
\{1, \ldots, r\}$. Suppose $e_i'+ 2\chi_J(i) = e_i$ where

@@

\begin{thm}
\label{thm:ramification_order_induction}
Suppose $(\sx', 0, L')$ is a tame separably rooted log stacky spin
curve is admissible with a generators $y_{i,e_i'} \in R' = R_{L'}$
as in (Ad-i) of Definition ~\ref{defn:admissible}. Then the
following are true:
\begin{enumerate}
	\item[(a)] For all $i \in J$, there exists $y_{i,e_i} \in
		H^0(\sx, e_i(K_\sx))$ so that
		\begin{align*}
			-ord_{Q_i}(y_{i,e_i}) = \frac{e_i-1}{2}
		\end{align*}
		and
		\begin{align*}
			\frac{-\ord_{Q_j}(y_{i,e_i'})}{y_{i,e_i}} \leq \subhalf{e_j'}-
			\frac{1}{\deg(y_{i,e_i'})e_j'}
		\end{align*}
		for all $j \in J$ with $j \neq i$.
	\item[(b)] The elements $y_{i,e_i'}^ay_{i,e_i}^b,$ with $a \geq 0,
		b > 0$ span $R$ over $R'$ and the elements $y_{i,e_i}$ minimally
		generate $R$ over $R'$.
	\item[(c)] Equip $k[y] = k[y_{i,e_i}]_{i \in J}$ and $k[x]$ with
		any graded monomial order and $k[y,x] = k[y] \otimes k[x]$ with
		block order. Let $R = k[y,x]/I.$ Then,
		\begin{align*}
			in_\prec(I) = in_\prec(I')k[x,y] + \langle y_{i,e_i}z \mid z \neq
			y_{i,e_i},y_{i,e_i'} \rangle
		\end{align*}
		as $z$ ranges over all generators of $R$.
	\item[(d)] Suppose $in_\prec(I')$ is minimally generated by
		products of two monomials and that for all $i \in J$, we have $e_i >
		\deg z$ for any generator $z$ of $R'.$ Then any set of minimal
		generators for $I'$ together with any set of relations as in part (c)
		minimally generate $I$.
	\item[(e)] For any $W \subset J,$ the set $(\sx,W)$ is admissible.
\end{enumerate}
\end{thm}

\begin{proof}
Let $(\sx, 0, L)$ and $(\sx', 0, L')$ be the two log stacky spin curves in 
question, with coarse spaces $X = X'$. 
\todo{possibly generalize these to arbitrary log stacky $\Delta \neq 0$ spin curves}
Define
